---
from: markdown+emoji
format:
  revealjs:
    logo: img/cesab-logo.png
    footer: "{{< fa brands github >}} &nbsp;<https://github.com/frbcesab/good-practices>"
    smaller: true
    auto-stretch: false
    toc-depth: 1
    theme: [default, "css/custom.scss"]
engine: knitr
---

```{r}
#| child: "slides/title-slide.qmd"
```


```{r}
#| child: "slides/introduction.qmd"
```


```{r}
#| child: "slides/data-management.qmd"
```


```{r}
#| child: "slides/project-organization.qmd"
```

```{r}
#| child: "slides/code-and-software.qmd"
```


```{r}
#| child: "slides/tracking-changes.qmd"
```


```{r}
#| child: "slides/collaboration.qmd"
```


```{r}
#| child: "slides/manuscript.qmd"
```






## Table of contents

:::: { .columns  }
::: { .column width="33%"}
**Data management**

**Project organization**

- RStudio project
- Build robust paths
- Naming things

- Research compendium
  - (Flexible) structure
  - The `DESCRIPTION` file
  - The folder `R/`
  - The `README`(s)
  
**Tracking changes**

- Version control system

**Collaboration**

- Code hosting platform
:::

::: { .column width="33%"}
**Optimization**

- Literate programming
- Functional programming
- Pipeline toolkit
  - `targets`
  - `makefile`
  
- R package
- Documentation
- Licensing

**Advanced tools**

- Managing dependencies (`renv`)
- CI/CD
  - GitHub actions
  - GitLab CI
- Docker
:::

::::




## Notes

<https://annakrystalli.me/talks/r-in-repro-research.html#1>

<https://library.seg.org/doi/abs/10.1190/1.1822162>

<https://inundata.org/talks/rstd19/#/>

<https://ropensci-archive.github.io/reproducibility-guide/sections/introduction/>

<https://insileco.io/workshop_reproducibility/#1>

<https://arxiv.org/pdf/1609.00037.pdf>

<https://ram.berkeley.edu/>

<https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.1001745#s5>

<https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005097>

<https://eliocamp.github.io/reproducibility-with-r/materials/day1/01-introduction/>

<https://www.youtube.com/watch?v=KHMW8fV2NXo>

<https://the-turing-way.netlify.app/reproducible-research/reproducible-research.html>

<https://annakrystalli.me/rrresearchACCE20/filenaming-view.html>

<https://allisonhorst.com/other-r-fun>
